Verifying Demonstrations

### 2018-03-02 paper/DB-anon-cred.tex

There is a protocol which provide \ac{DBPK} with all the desired properties from above, ProProx~\cite{ProProx}.
(Note that~\cite{ProProx} uses the abbreviation PoPoK, for Proof of Proximity of Knowledge.)
However, ProProx provides \iac{DBPK} protocol only for quadratic residues (\ie for proving \(\DBPK[\alpha][a = \alpha^2]\)) while in our context, we need a \iac{DBPK} protocol for discrete logarithms.
To realize this, we will now introduce such a protocol that will allow us to do \ac{DB} anonymous credentials.
We note, however, that this protocol only provides \ac{DBMF}, \ac{DBDF}, \ac{DBDH} and \ac{DBIF} resistance --- but not \ac{DBTF} resistance.

@@

\emph{New attempt of \iacl{DB} Schnorr protocol.} In the original \ac{DB} paper by \citet{DistanceBounding}, they show how to design a distance bounding protocol based on the Schnorr identification scheme~\cite{Schnorr}.
That \ac{DB} Schnorr protocol was shown to be prone to distance 
hijacking~\cite{DistanceHijacking}.
We now propose another way to turn the Schnorr protocol into \iac{DB} protocol 
which is secure against \ac{DBIV}, \ac{DBMF}, \ac{DBDF} and \ac{DBDH}.
It will not protect against terrorist fraud, although ideally this property should be desirable.

>>>>

There is a protocol which provide \ac{DBPK} with all the desired properties from 
above, ProProx~\cite{ProProx}.
(Note that~\cite{ProProx} uses the abbreviation PoPoK, for Proof of Proximity of 
Knowledge, instead of \ac{DBPK}.)
However, ProProx provides \iac{DBPK} protocol for quadratic residues (\ie for 
proving \(\DBPK[\alpha][a = \alpha^2]\)) while in our context, we need 
\iac{DBPK} protocol for discrete logarithms.
To realize this, we will now introduce such a protocol that will allow us to do 
\ac{DB} anonymous credentials.
We note, however, that this protocol only provides \ac{DBMF}, \ac{DBDF}, 
\ac{DBDH} and \ac{DBIF} resistance --- but not \ac{DBTF} resistance.

@@

\emph{Reattempting \iacl{DB} Schnorr protocol.}
In the original \ac{DB} paper by \citet{DistanceBounding}, they show how to 
design a distance-bounding protocol based on the Schnorr identification 
scheme~\cite{Schnorr}.
That \ac{DB} Schnorr protocol was shown to be prone to distance 
hijacking~\cite{DistanceHijacking}.
We now propose another way to turn the Schnorr protocol into \iac{DB} protocol 
which is secure against \ac{DBIV}, \ac{DBMF}, \ac{DBDF} and \ac{DBDH}.
It will not protect against terrorist fraud, although ideally this property should be desirable.

### 2018-03-02 paper/TimeStamp.tex

\subsection{Time-stamping service, or, blockchains}%
\label{StorageProperties}

@@

We can instantiate \(\TS\) using a blockchain, \eg OmniLedger~\cite{OmniLedger}.
The \(\TSstamp[x]\) algorithm will simply include \(x\) in the blockchain and 
return the block into which \(x\) was included.
\(\TSget\) will return the hash of the current head of the chain.
This value is difficult to predict since it depends on all submitted 
transactions and usually some randomness, \eg nonces and miners' secrets.
The blockchain must also be continuously extended, \eg as in
Bitcoin~\cite{Bitcoin}, where a new block appears approximately every 10 
minutes.
So having a dedicated blockchain for a protest will not do, it is better to use 
a blockchain which is also used for other things too.

There are some additional properties that we need from \(\TS\), which are 
implied by blockchains.
First, we need immutability, \ie once we commit something (through \(\TSstamp\)) 
it will remain there.
We will use this to ensure verifiability, the data must remain to be verifiable.

Second, once we have committed some data, we do not need to keep the data 
itself, but we can store some confirmation value instead.
\Eg using blockchains, we can store the hash of the block where our data was 
committed, while this block remains we are sure that our data remains committed 
--- even if we no longer remember what our data looked like.
We will use this property to approximate the property of receipt freeness.

>>>>

\subsection{Time-stamping service -- blockchains}%
\label{StorageProperties}

@@

We can instantiate \(\TS\) using a blockchain, \eg OmniLedger~\cite{OmniLedger}.
The \(\TSstamp[x]\) algorithm will simply include \(x\) in the blockchain and return the block into which \(x\) was included.
\(\TSget\) will return the hash of the current head of the chain.
This value is difficult to predict since it depends on all submitted transactions and usually some randomness (\eg nonces and miners' secrets).
The blockchain must also be continuously extended, such as in Bitcoin~\cite{Bitcoin}, in which a new block appears approximately every 10 minutes.
Having a dedicated blockchain for a protest will not do, and thus it is better to use a blockchain which is also used for other things too.

There are some additional properties that we need from \(\TS\), which are implied by blockchains.
First, we need \emph{immutability}, to ensure that once we commit something (through \(\TSstamp\)) it will remain there.
We will use this to ensure verifiability as the data must remain to be verifiable.
Second, once we have committed some data, we do not need to keep the data itself, but we can store some confirmation value instead.
For instance using blockchains, we can store the hash of the block in which our data was committed, while this block remains we are sure that our data remains committed --- even if we no longer remember what our data looked like.
We will use this property to approximate the property of receipt freeness.

### 2018-03-02 paper/conclusions.tex

We have introduced \PRIVO, a protocol for verifiably counting
participants at protests. Despite the verification, the privacy of the
participants is preserved to the extent possible by their physical
presence at the protest. To achieve that, we adapted the Schnorr
protocol to develop distance-bounding anonymous credentials. Except for receipt
freeness (\cref{ReceiptFreeness}), which we cannot guarantee if the adversary gets access to
Alice's device and cryptographic secret, \PRIVO
fulfills all verification and privacy properties we derived from those
of electronic voting complemented by the specific constraints on time
and location required for protests. 
In general, none of the related works fulfills the eligibility verifiability 
\cref{%
  CountOnce,%
  CreatedAfterStart,CreatedBeforeEnd,SpatiallyRelated,%
}.
To some extent, some techniques do fulfill \cref{DesignatedEvent}, since people 
usually use placards in the protests.
Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but 
not individual verifiability (\cref{IndividualVerif}).
If they would provide individual verifiability, they would likely violate the 
privacy requirements.

>>>>

We have introduced \PRIVO, a protocol for verifiably counting
participants at protests. Despite the verification, the privacy of the
participants is preserved to the extent possible by their physical
presence at the protest. To achieve that, we adapted the Schnorr
protocol to develop distance-bounding anonymous credentials. Except for receipt
freeness (\cref{ReceiptFreeness}), which we cannot guarantee if the adversary gets access to
Alice's device and secret PRF key after her participation has
been witnessed and before she had a chance to
delete it, \PRIVO
fulfills all verification and privacy properties we derived from those
of electronic voting complemented by the specific constraints on time
and location required for protests. 
In general, none of the related works fulfills the eligibility verifiability 
\cref{%
  CountOnce,%
  CreatedAfterStart,CreatedBeforeEnd,SpatiallyRelated,%
}.
To some extent, some techniques do fulfill \cref{DesignatedEvent}, since people 
usually use placards in the protests.
Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but 
not individual verifiability (\cref{IndividualVerif}).
If they would provide individual verifiability, they would likely violate the 
privacy requirements.
